Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-27 analysis/paper_draft3.Rmd
minor edits, insert cross-reference to first mention of Fig. 1

A _Batson_ challenge typically proceeds in a four-step sequence (Figure 1). First, the attorney must decide whether to challenge the opposing attorney's use of one or more peremptory strikes as based on illegal bias. Second, if challenged, the challenger must meet an initial burden (the _prima facie_ case) of producing just enough evidence of strike bias to raise a sufficient initial inference of illegal bias. Third, the striking attorney must proffer permissible reasons for their challenged strikes. Fourth, the challenger must discredit those proffered reasons and ultimately persuade the trial judge that it is more likely than not that the striking attorney acted with illegal bias.

@@

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and based on historical strike data for that attorney.

>>>>

A _Batson_ challenge typically proceeds in a four-step sequence (Figure \@ref(fig:batsonworkflowfig)). First, the attorney must decide whether to challenge the opposing attorney's use of one or more peremptory strikes as based on illegal bias. Second, if challenged, the challenger must meet an initial burden (the _prima facie_ case) of producing just enough evidence of strike bias to raise a sufficient initial inference of illegal bias. Third, the striking attorney must proffer permissible reasons for their challenged strikes. Fourth, the challenger must discredit those proffered reasons and ultimately persuade the trial judge that it is more likely than not that the striking attorney acted with illegal bias.

@@

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and such values based on historical strike data for that attorney.
